### 2018-10-04 CWP/papers/HSF-CWP-2017-14_recotrigger/latex/recoCWP.tex
Tex sources for reco & trigger chapter (#102)
* Add files via upload

* Move LaTeX files into standard subdirectory

* Add gitignore for generated PDFs

* Remove unneeded a2tex script

\documentclass[11pt,letterpaper,fleqn]{article}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{afterpage}
\usepackage{pdflscape}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  citecolor=blue
}
\usepackage{subfigure}
\usepackage{cite}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}
\usepackage{enumitem} %%% uncommenting this line and associated
%% options only saves about 1/4 page
% enumitem options
%\setlist{nosep}
%\setitemize{wide}
%\setlist\bibitem{itemize}{leftmargin=*}
%\setlist\bibitem{enumerate}{leftmargin=*}

@@

\input{titlepageFull.tex}
\newpage
%\tableofcontents
%\newpage
\setcounter{page}{1}

\input{allFull.tex}

@@

\begin{thebibliography}{99}

@@

%\bibitem{RECOCWP}
%Software trigger and event reconstruction CWP group, To be published (\href{https://docs.google.com/document/d/1QRO8RA488fwfSg5CSjmvm16-pZpGApSA0l666g_mS_0}{Link}).

@@

\bibitem{Bordry2016} 
F. Bordry, 
\textit{presentation at the LHC Performance Workshop (Chamonix 2016)}, 
January 25th - 28th, 2016. (\href{http://chamonix-2016.web.cern.ch/}{Link} and \href{http://lhc-commissioning.web.cern.ch/lhc-commissioning/schedule/LHC-schedule-update.pdf}{Link})

\bibitem{LHCb2012} 
LHCb Collaboration, 
\textit{LHCb upgrade framework TDR},  
CERN-LHCC-2012-007 (2012) (\href{https://cds.cern.ch/record/1443882}{Link}).

\bibitem{ALICE2013} 
A. Kluge et al., 
\textit{Upgrade of the ALICE Readout and Trigger System}, 
CERN-LHCC-2013-019 (\href{https://cds.cern.ch/record/1603472}{Link}).

\bibitem{Zimmerman2009} 
F. Zimmerman, PoS EPS-HEP2009, 140 (2009). 
G. Apollinari et al., 
\textit{High-Luminosity Large Hadron Collider (HL-LHC): Preliminary Design Report}, 
CERN-2015-005.%, doi:10.5170/CERN-2015-005.

@@

\bibitem{LHCb2017} 
LHCb Collaboration, 
\textit{Expression of Interest for a Phase-II LHCb Upgrade: Opportunities in flavour physics, and beyond, in the HL-LHC era},  
CERN-LHCC-2017-003 (2017) (\href{https://cds.cern.ch/record/2244311}{Link}).

\bibitem{Ohnishi2013} 
Y. Ohnishi, et. al., 
\textit{Accelerator design at SuperKEKB}, 
Prog. Theor. Exp. Phys. 2013 03A011 (2013) (\href{http://dx.doi.org/10.1093/ptep/pts083}{Link}).

\bibitem{BelleII2010} 
Belle II Collaboration, 
\textit{Belle II Technical Design Report}, 
KEK Report 2010-1 (2010) (\href{https://arxiv.org/abs/1011.0352}{Link}).

\bibitem{DUNE2016} 
DUNE Collaboration, 
\textit{Long-Baseline Neutrino Facility (LBNF) and Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report Volume 1: The LBNF and DUNE Projects}, 
arXiv:1601.05471 (2016) (\href{https://arxiv.org/abs/1601.05471}{Link}).

\bibitem{Ball2014} 
A. Ball et al., 
\textit{Future Circular Collider Study Hadron Collider Parameters}, 
FCC-ACC-SPC-0001 1342402, CERN (2014) (\href{https://indico.cern.ch/event/298180/contributions/1658149/attachments/560575/772288/FCC-1401101315-DSC_HadronColliderParameters_V0.3.pdf}{Link}).

\bibitem{Ilten2016} 
P. Ilten, Y. Soreq, J. Thaler, M. Williams, and W. Xue, 
\textit{Proposed inclusive dark photon search at LHCb}, 
Phys. Rev. Lett. 116, 251803 (2016).

\bibitem{aTLAs2017}
%ATLAS Collaboration, \textit{Performance of the ATLAS Trigger System in 2015} ,
%Eur. Phys. J.C77 5 317 (2017),
%\href{https://inspirehep.net/record/1500696}{Link}. 
ATLAS Collaboration,
\textit{Trigger-object Level Analysis with the ATLAS detector at the Large Hadron Collider: summary and perspectives}, 
ATL-DAQ-PUB-2017-003 (2017) (\href{https://cds.cern.ch/record/2295739}{Link}).

@@

\bibitem{Marshall2015} The Pandora Software Development Kit for Pattern Recognition
J.S. Marshall, M.A. Thomson (Cambridge U.). Jun 16, 2015. 15 pp.
Published in Eur.Phys.J. C75 (2015) no.9, 439

\bibitem{Gray2016} 
L. Gray, 
\textit{Challenges of Particle Flow reconstruction in the CMS High-Granularity Calorimeter at the High-Luminosity LHC}, 
38th International Conference on High Energy Physics (ICHEP 2016), (\href{https://indico.cern.ch/event/432527/contributions/1071751/}{Link}).

\bibitem{Gray2017} 
L. Gray, 
\textit{4 Dimensional Trackers},
(2017) (\href{https://indico.cern.ch/event/577003/contributions/2476434}{Link}).

\bibitem{ATLAS2015} 
ATLAS Collaboration, 
\textit{ATLAS Phase-II Upgrade Scoping Document}, 
CERN-LHCC-2015-020, LHCC-G-166 (2015) (\href{https://cds.cern.ch/record/2055248}{Link})

\bibitem{Abreu2014} 
R. Abreu, 
\textit{The upgrade of the ATLAS High Level Trigger and Data Acquisition systems and their integration}, 
Proceedings of 19th IEEE-NPSS Real-Time conference 2014, pp.7097414 (2014) (\href{https://cds.cern.ch/record/1702466/}{Link}).

\bibitem{Petrucciani2015} 
G. Petrucciani et. al., 
\textit{Mini-AOD: A New Analysis Data Format for CMS}, Journal of Physics: Conference Series 664 7 072052 (2015)

\bibitem{Eifert2015} 
T. Eifert, et. al., 
\textit{Implementation of the ATLAS Run 2 event data model}, 
Journal of Physics: Conference Series, Volume 664, Offline software (2015) (\href{http://iopscience.iop.org/article/10.1088/1742-6596/664/7/072045}{Link}).

\bibitem{Allton2017} 
C. Allton, et. al.,  
\textit{Computing Resources Scrutiny Group}, 
CERN–RRB–2017–056 (2017) (\href{https://indico.cern.ch/event/617821/contributions/2493341/attachments/1446478/2233022/CERN-RRB-2017-056_V2.pdf}{Link}).

\bibitem{DUNE2015}, 
Dune Collaboration, 
\textit{LBNF/DUNE Conceptual Design Report, Annex 4B Expected Data Rates for the DUNE Detectors}, 
(2015) (\href{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=10720}{Link}).

\bibitem{DUNE2017}, 
Dune Collaboration, 
\textit{The Single-Phase ProtoDUNE Technical Design Report},
(2017) (\href{https://arxiv.org/abs/1706.07081}{Link}).

\bibitem{Miyamoto2015} 
A.Miyamoto et al., 
\textit{Computing Requirements of the ILC Experiments}, 
LCC-Note (2015), (\href{http://www-jlc.kek.jp/~miyamoto/SoftwareCommonTask/docs/ILCComputing-EDMS1130485.A.1.1.pdf}{Link})

\bibitem{Richter2016} 
M. Richter, 
\textit{Online Data Compression in the ALICE O2 Facility}, 
Presented at the Computing in High Energy and Nuclear Physics conference (2016),
\href{https://indico.cern.ch/event/505613/contributions/2227264/}{Link}.

\bibitem{ATLASTwiki} 
\href{https://twiki.cern.ch/twiki/pub/AtlasPublic/TriggerOperationPublicResults/BandwidthPie2016.png}{BandwidthPie2016.png}, 
\href{https://twiki.cern.ch/twiki/pub/AtlasPublic/TriggerOperationPublicResults/Time_HLTRate_Stack_2016_07.png}{Time\_HLTRate\_Stack\_2016\_07.png}

\bibitem{CMS2014} 
CMS Collaboration, 
\textit{Description and performance of track and primary-vertex reconstruction with the CMS tracker},  
JINST 9 (2014) 10009 (\href{http://cds.cern.ch/record/1704291}{Link}).

\bibitem{CMS2017} 
CMS Collaboration, 
\textit{Particle-flow reconstruction and global event description with the CMS detector}, 
Submitted to JINST (2017) (\href{https://arxiv.org/abs/1706.04965}{Link}).

\bibitem{LHCbRTCalib2016} 
G. Dujani and B. Storaci, 
\textit{Real-time alignment and calibration of the LHCb Detector in Run II}, 
Journal of Physics: Conference Series, Volume 664, Online computing (\href{https://cds.cern.ch/record/2017839?ln=en}{Link}).

%\bibitem{Brun1996}
%R. Brun and F. Rademakers,
%\textit{ROOT - An Object Oriented Data Analysis Framework}, 
%Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996, Nucl. Inst. \& Meth. in Phys. Res. A 389 (1997) 81-86. See also \href{http://root.cern.ch}{ROOT homepage}.

@@

\input{appendix.tex}

>>>>

\documentclass[11pt,letterpaper,fleqn]{article}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  citecolor=blue
}
\usepackage{subfigure}
\usepackage{cite}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}
\usepackage{enumitem} %%% uncommenting this line and associated
%% options only saves about 1/4 page
% enumitem options
%\setlist{nosep}
%\setitemize{wide}
%\setlist[itemize]{leftmargin=*}
%\setlist[enumerate]{leftmargin=*}

@@

\input{titlepage.tex}
\newpage
%\tableofcontents
%\newpage
\setcounter{page}{1}

\input{all.tex}

@@

\begin{thebibliography}{9}

@@

\bibitem{RECOCWP}
Software trigger and event reconstruction CWP group, To be published as HSF-CWP-2017-16 (\href{https://github.com/HEP-SF/documents/tree/master/CWP/papers}{Link}).

@@

@@

\bibitem{Brun1996}
R. Brun and F. Rademakers,
\textit{ROOT - An Object Oriented Data Analysis Framework}, 
Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996, Nucl. Inst. \& Meth. in Phys. Res. A 389 (1997) 81-86. See also \href{http://root.cern.ch}{ROOT homepage}.

\bibitem{ATLAS2017}
ATLAS Collaboration, \textit{Performance of the ATLAS Trigger System in 2015} ,
Eur. Phys. J.C77 5 317 (2017),
\href{https://inspirehep.net/record/1500696}. ATLAS Collaboration,
\textit{Trigger-object Level Analysis with the ATLAS detector at the Large Hadron Collider: summary and perspectives}, 
ATL-DAQ-PUB-2017-003 (2017) (\href{https://cds.cern.ch/record/2295739}{Link}).

@@

@@
